SVG: The Paper

### 2022-06-07 Analysis/index.Rmd
Adding predictions to init_sel model

create_post_plot("x") + create_post_plot("y") 
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

>>>>

create_post_plot("x") + create_post_plot("y") 
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```
How well does the model do in guessing the first target in a trial?

```{r}
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  mutate(x = if_else(x < 0.01, 0.01, x),
         x = if_else(x > 0.99, 0.99, x),
         y = if_else(y < 0.01, 0.01, y),
         y = if_else(y > 0.99, 0.99, y) ) %>%
  select(-RT)

get_model_weight <- function(obs, cond, trl) {

  dt <- filter(d, observer == obs, condition == cond, trial == trl)

  mtx <- filter(am, observer == obs, dim == "x")
  mty <- filter(am, observer == obs, dim == "y")

  wx <- dbeta(dt$x, mtx$a, mtx$b)
  wy <- dbeta(dt$y, mty$a, mty$b)
  w <- wx * wy
  w <- w / sum(w)

  return(tibble(observer = obs,
                condition = cond, 
                trial = trl,
                init_weight = w[1],
                max_item = which(w == max(w))))
}

d %>% group_by(observer, condition, trial) %>%
  summarise(n = n(), .groups = "drop") %>%
  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
  pmap_df(get_model_weight) -> weights

ggplot(weights, aes(init_weight)) + geom_histogram(binwidth = 1/80) +
  geom_vline(xintercept = 1/40, linetype = 2) -> plt1

weights %>% group_by(observer) %>%
  summarise(acc = mean(max_item == 1)) %>%
  ggplot(aes(y = acc)) + geom_boxplot() + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") -> plt2

plt1 + plt2
```
